### 2016-07-17 P4-Explore-and-Summarize-Data/submission.Rmd
Update submission.Rmd

# Bivariate Plots Section
```{r , Bivariate_Plots}
bivariate_plot <- function(y, ylab) {
  return (qplot(data = rw, x = '', y = y, 
                geom = 'boxplot', 
                xlab = '', 
                ylab = ylab))
}

grid.arrange(bivariate_plot(rw$fixed.acidity, 'fixed.acidity (g / dm^3)'),
             bivariate_plot(rw$volatile.acidity, 'volatile.acidity (g / dm^3)'),
             bivariate_plot(rw$citric.acid, 'citric.acid (g / dm^3)'),
             bivariate_plot(rw$residual.sugar, 'residual.sugar (g / dm^3)'),
             bivariate_plot(rw$chlorides, 'chlorides (g / dm^3)'),
             bivariate_plot(rw$free.sulfur.dioxide, 'free.sulfur.dioxide (mg / dm^3)'),
             bivariate_plot(rw$total.sulfur.dioxide, 'total.sulfur.dioxide (mg / dm^3)'),
             bivariate_plot(rw$density, 'density (g / cm^3)'),
             bivariate_plot(rw$pH, 'pH'),
             bivariate_plot(rw$sulphates, 'sulphates (g / dm^3)'),
             bivariate_plot(rw$alcohol, 'alcohol (% volume)'),
             ncol = 4)
```

@@

```{r }
quality_plot <- function(x, y, ylab) {
  return (ggplot(data = rw, aes(x, y)) +
           geom_boxplot(fill = 'green') +
            xlab('quality') +
            ylab(ylab))
}

@@

```{r , Multivariate_Plots}
ggplot(data = rw, aes(pH, alcohol, color = quality)) +
  geom_point() +
  facet_wrap(~rating) +
  ylab('alcohol (% volume)')

ggplot(data = rw, aes(alcohol, citric.acid, color = quality)) +
  geom_point() +
  facet_wrap(~rating) +
  xlab('alcohol (% volume)') +
  ylab('citric.acid (g / dm^3)')

ggplot(data = rw, aes(alcohol, sulphates, color = quality)) +
  geom_point() +
  facet_wrap(~rating) +
  xlab('alcohol (% volume)') +
  ylab('sulphates (g / dm^3)')

ggplot(data = rw, aes(citric.acid, fixed.acidity, color = quality)) +
  geom_point() +
  facet_wrap(~rating) +
  xlab('citric.acid (g / dm^3)') +
  ylab('fixed.acid (g / dm^3)')
```

@@

### Plot Three : Effect of pH on wine quality
```{r , Plot_Three}
ggplot(data = rw, aes(log10(total.acidity), pH)) +
  geom_point(alpha = 1/10) +
  scale_x_continuous() +
  geom_smooth() +
  xlab('total.acidity (g / dm^3)') +
  ggtitle('pH Relation on Wine Quality')

### Description Three
From the above plot, it shows there is linear relationships between pH and total.acidity. This means lower the pH, more acidic the wines. This also substantiate that higher the acidic tends to better the wine.

### Plot Four : Ideal vs poor wine

@@

### Description Four
It would be great to see the real pattern between good and bad wines. Above plot differentiate between good and bad wines. It shows higher the % of alcohol and higher the sulphates give better wines.

>>>>

# Bivariate Plots Section

@@

```{r }
quality_plot <- function(x, y, ylab) {
  return (ggplot(data = rw, aes(x, y)) +
           geom_boxplot(fill = 'green') +
            xlab('quality') +
            ylab(ylab) + 
            facet_wrap(~quality))
}

@@

```{r , Multivariate_Plots}
ggplot(data = rw, aes(pH, alcohol, color = as.factor(quality))) +
  geom_point() +
  facet_wrap(~rating) +
  ylab('alcohol (% volume)') +
  theme_dark() +
  scale_color_brewer(type = 'seq', palette = 1)

ggplot(data = rw, aes(alcohol, citric.acid, color = as.factor(quality))) +
  geom_point() +
  facet_wrap(~rating) +
  xlab('alcohol (% volume)') +
  ylab('citric.acid (g / dm^3)') +
  scale_color_brewer(type = 'seq', palette = 2) +
  theme_dark()

ggplot(data = rw, aes(alcohol, sulphates, color = as.factor(quality))) +
  geom_point() +
  facet_wrap(~rating) +
  xlab('alcohol (% volume)') +
  ylab('sulphates (g / dm^3)') +
  scale_color_brewer(type = 'seq', palette = 3) +
  theme_dark()

ggplot(data = rw, aes(citric.acid, fixed.acidity, color = as.factor(quality))) +
  geom_point() +
  facet_wrap(~rating) +
  xlab('citric.acid (g / dm^3)') +
  ylab('fixed.acid (g / dm^3)')  +
  scale_color_brewer(type = 'seq', palette = 4) +
  theme_dark()
```

@@

### Plot Three : Ideal vs poor wine

@@

### Description Three
It would be great to see the real pattern between good and bad wines. Above plot differentiate between good and bad wines. It shows higher the % of alcohol and higher the sulphates give better wines.
